<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{Getting started with Personfit in PP}
-->
# Getting started with Person-Fit functions

A brief introduction in the currently implemented person fit functions will be added soon. Currently the **LZ, LZ*** and also the **Infit-Outfit-Statistics** are implemented. We also added the Infit-Outfit-Functions for the Partial-Credit Model. Meanwhile we are working on plots for a better understanding of the person misfit as well as on inference statistic methods.

```{r settings}
knitr::opts_chunk$set(message = FALSE, results='hide')
```

Now a simple example will be given.
First, we will simulate some data for our hands on example:
```{r start}
library(PP)

set.seed(1337)

# simulate some intercepts
diffpar <- seq(-3,3,length=15)
# simulate some slope parameters
sl     <- round(runif(15,0.5,1.5),2)
la     <- round(runif(15,0,0.25),2)
ua     <- round(runif(15,0.8,1),2)

# simulate response matrix
awm <- matrix(sample(0:1,100*15,replace=TRUE),ncol=15)
```

We will start with a simple 1PL-Model. First, we have to estimate the person parameters. Here we have to choose an estimation method. It is important, that you can choose **mle, wle or map** only for the LZ and LZ* Index. For the Infit-Outfit statistic we support **mle and wle** estimates.

```{r 1pl}
# MLE
res1plmle <- PP_4pl(respm = awm,thres = diffpar,type = "mle")
# WLE
res1plwle <- PP_4pl(respm = awm,thres = diffpar,type = "wle")
# MAP estimation
res1plmap <- PP_4pl(respm = awm,thres = diffpar,type = "map")
```

We also support the 2PL, 3PL and 4PL Model:
```{r 234-pl}

# ------------------------------------------------------------------------
## 2PL model ##### 
# ------------------------------------------------------------------------
# MLE
res2plmle <- PP_4pl(respm = awm,thres = diffpar, slopes = sl,type = "mle")
# WLE
res2plwle <- PP_4pl(respm = awm,thres = diffpar, slopes = sl,type = "wle")

# ------------------------------------------------------------------------
## 3PL model ##### 
# ------------------------------------------------------------------------
# MLE
res3plmle <- PP_4pl(respm = awm,thres = diffpar,
                    slopes = sl,lowerA = la,type = "mle")
# WLE
res3plwle <- PP_4pl(respm = awm,thres = diffpar,
                    slopes = sl,lowerA = la,type = "wle")
# ------------------------------------------------------------------------
## 4PL model ##### 
# ------------------------------------------------------------------------
# MLE
res4plmle <- PP_4pl(respm = awm,thres = diffpar,
                    slopes = sl,lowerA = la,upperA=ua,type = "mle")
# WLE
res4plwle <- PP_4pl(respm = awm,thres = diffpar,
                    slopes = sl,lowerA = la,upperA=ua,type = "wle")
```

After the estimation of the person parameter we are able to calculate the person fits. At this point you are able to calculate only one kind of personfit as well as all simultaneously (as shown next).

```{r pfit}

# ------------------------------------------------------------------------
## 1PL model ##### 
# ------------------------------------------------------------------------
## LZ*-Index ##### 
pfit1pl_lz <- Pfit(respm=awm,pp=res1plwle,fitindices="lzstar")
## LZ*-Index combined with Infit-Outfit ##### 
pfit1pl_li <- Pfit(respm=awm,pp=res1plwle,fitindices=c("lzstar","infitoutfit"))
# ------------------------------------------------------------------------
## 2PL model ##### 
# ------------------------------------------------------------------------
## LZ*-Index ##### 
pfit2pl_lz <- Pfit(respm=awm,pp=res2plwle,fitindices="lzstar")
## LZ*-Index combined with Infit-Outfit ##### 
pfit2pl_li <- Pfit(respm=awm,pp=res2plwle,fitindices=c("lzstar","infitoutfit"))
# ------------------------------------------------------------------------
## 3PL model ##### 
# ------------------------------------------------------------------------
## LZ*-Index ##### 
pfit3pl_lz <- Pfit(respm=awm,pp=res3plwle,fitindices="lzstar")
## LZ*-Index combined with Infit-Outfit ##### 
pfit3pl_li <- Pfit(respm=awm,pp=res3plwle,fitindices=c("lzstar","infitoutfit"))
# ------------------------------------------------------------------------
## 4PL model ##### 
# ------------------------------------------------------------------------
## LZ*-Index ##### 
pfit4pl_lz <- Pfit(respm=awm,pp=res4plwle,fitindices="lzstar")
## LZ*-Index combined with Infit-Outfit ##### 
pfit4pl_li <- Pfit(respm=awm,pp=res4plwle,fitindices=c("lzstar","infitoutfit"))
```

We can also use different person parameter estimates.

```{r wle}
# ------------------------------------------------------------------------
## 1PL model ##### 
# ------------------------------------------------------------------------
## LZ*-Index ##### 
## mle ####
pfit1pl_mle_l <- Pfit(respm=awm,pp=res1plmle,fitindices="lzstar")
## wle ####
pfit1pl_wle_l <- Pfit(respm=awm,pp=res1plwle,fitindices="lzstar")
## map ####
pfit1pl_map_l <- Pfit(respm=awm,pp=res1plmap,fitindices="lzstar")
```
